Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-04 Experiments.tex
space saving. 5 lines over.

Each experiment entails executing multiple instances of AthenaMP using the NGE
to simulate a pre-determined number of events. All the experiments have been
performed by  configuring AthenaMP to use all the 16 cores  of Titan's worker
nodes.

We  measured the execution time of the pilots and of the AthenaMP  executed
within them, collecting timestamps at  all stages of the execution. Experiments
have been performed  by  submitting NGE's pilots  to Titan's batch queue.  The
turnaround time of an individual run is determined by queue waiting times. Since
we are interested only in the performances of the NGE, we removed queue time
from our statistics.

>>>>

Each experiment entails executing multiple instances of AthenaMP 
to simulate a pre-determined number of events. All the experiments have been
performed by  configuring AthenaMP to use all the 16 cores  of Titan's worker
nodes.

We  measured the execution time of the pilots and of AthenaMP 
within them, collecting timestamps at  all stages of the execution. Experiments
were performed  by  submitting NGE's pilots  to Titan's batch queue.  The
turnaround time of an individual run is determined by queue waiting times. Since
we are interested only in the performances of the NGE, we removed queue time
from our statistics.

### 2017-04-04 conclusion.tex
space saving. 5 lines over.

We characterized the state of practice by evaluating the efficiency, scalability
and reliability of both PanDA Broker and AthenaMP as deployed on Titan
(\S\ref{sec:panda_titan}). Our characterization highlighted both the strengths
and limitations of the current design and implementation: PanDA Brokers enable
the sustained execution of millions of simulations per week but further work is
required to optimize its efficiency and reliability (\S\ref{ssec:broker_titan}).
PanDA Brokers support the concurrent execution of multiple AthenaMP instances,
enabling each AthenaMP to perform the concurrent execution of up to 16 Geant4
simulators. Nonetheless, our characterization showed how improving I/O
performance could reduce overheads (\S\ref{ssec:athenamp_titan}), increasing the
overall utilization of Titan's backfill availability.

>>>>

We characterized the state of practice by evaluating the efficiency, scalability
and reliability of both PanDA Broker and AthenaMP as deployed on Titan
(\S\ref{sec:panda_titan}). Our characterization highlighted the strengths
and limitations of the current design and implementation: PanDA Brokers enable
the sustained execution of millions of simulations per week but further work is
required to optimize its efficiency and reliability (\S\ref{ssec:broker_titan}).
PanDA Brokers support the concurrent execution of multiple AthenaMP instances,
enabling each AthenaMP to perform the concurrent execution of up to 16 Geant4
simulators. Nonetheless, our characterization showed how improving I/O
performance could reduce overheads (\S\ref{ssec:athenamp_titan}), increasing the
overall utilization of Titan's backfill availability.

### 2017-04-04 nge.tex
space saving. 5 lines over.

NGE is a runtime system to execute heterogeneous and dynamically determined
tasks that constitute workloads. Fig.~\ref{fig:arch-overview} illustrates its
current architecture as deployed on Titan: the two management modules (Pilot
and Unit) represent a simplified version of the PanDA Broker while the agent
module is the pilot submitted to Titan and executed on its worker nodes. The
communication between PanDA Broker and PanDA Server is abstracted away as it
is not immediately useful to evaluate the performance and capabilities of a
pilot on Titan.

>>>>

NGE is a runtime system to execute heterogeneous and dynamically determined
tasks that constitute workloads. Fig.~\ref{fig:arch-overview} illustrates its
current architecture as deployed on Titan: the two management modules (Pilot
and Unit) represent a simplified version of the PanDA Broker while the agent
module is the pilot submitted to Titan and executed on its worker nodes. The
communication between PanDA Broker and Server is abstracted away as it
is not immediately useful to evaluate the performance and capabilities of a
pilot on Titan.
